---
title: "1.4 Stationary Time Series"
author: "Nick Wintz"
output: 
  html_notebook:
    theme: flatly
    toc: yes
    toc_depth: 2
---

#Stationary Time Series
##White Noise

>**Example (White Noise):** Let $W_t\sim WN(0,1)$. Here, consider 100 iterations.


```{r, fig.height = 10, fig.width = 9}
set.seed(100); # This allows us to reproduce our results

par(mfrow=c(2,1)) #This gives us our graphs in 2 rows, 1 column

n=seq(1,100,1) #This gives our iterations starting from n=1 to n=100, with a step size of 1
WN=rnorm(100,0,1); #Here is the White Noise. rnorm(n,mean,std dev)
plot(n,WN,type="o",col="blue",main="White Noise",ylab=expression(W[t]),xlab="Time") #This plots the white noise

acf(WN, main="") #This plots the ACF. main="" turns the title off
```

##MA(1) Models
>**Example (MA(1) Models):** Let $X_t=W_t+0.6W_{t-1}$, where $W_t\sim WN(0,1)$. Here, we consider 320 iterations. To avoid any startup issues, we delete the first 20 iterations.

```{r, fig.height = 10, fig.width = 9}
set.seed(100) ;# This allows us to reproduce our results
par(mfrow=c(2,1)) #This gives us our graphs in 2 rows, 1 column

w<-rnorm(320,0,1) #noise with 20 extra iterations to avoid startup issues  
v<-filter(w, sides=1, c(1,.6))[-(1:20)] #MA(1). The c term represents the coefficients and the last term removes the first 20 iterations
plot.ts(v, main="MA(1)",col="blue",ylab=expression(X[t]),xlab="Time") #This plot the MA(1) model

acf(v, main="") #This plots the ACF.
```

##AR(1) Models
>**Example (AR(1) Models):** Let $X_t=0.6X_{t-1}+W_{t}$, where $W_t\sim WN(0,1)$. Here, we consider 320 iterations. To avoid any startup issues, we delete the first 20 iterations.

```{r, fig.height = 10, fig.width = 9}
set.seed(100); # This allows us to reproduce our results
par(mfrow=c(2,1)) #This gives us our graphs in 2 rows, 1 column

w<-rnorm(320,0,1) #noise with 20 extra iterations to avoid startup issues 
y<-filter(w, filter=c(.6), method="recursive")[-(1:20)] #AR(1). The c term represents the coefficients and the last term removes the first 20 iterations
plot.ts(y, main="AR(1)",col="blue",ylab=expression(X[t]),xlab="Time") #This plot the MA(1) model
acf(y,main="") #This plots the ACF.

```

#Nonstationary Time Series
##Nonconstant Trend
>**Example (Nonconstant Trend):** Let $X_t=1+0.1t+Y_{t}$, where $Y_t\sim WN(0,4)$. Let's use 100 iterations.

```{r, fig.height = 10, fig.width = 9}
set.seed(100); # This allows us to reproduce our results

par(mfrow=c(2,1)) #This gives us our graphs in 2 rows, 1 column
t=seq(1,100,1); #This gives our iterations starting from t=1 to t=100, with a step size of 1
Mt<-1+.1*t; #Linear Trend
Yt<-rnorm(length(t),0,2) #Y_t\sim WN(0,4)
Xt<-Mt+Yt #Time series with linear trend
plot.ts(Xt,type="o",xlab="Time",ylab=expression(X[t]),main="Nonconstant Trend") #This plots the time series with a nonconstant trend
lines(t,Mt,col="red") #This is the graph of linear trend itself
acf(Xt, main="") #This plots the ACF

```


##Seasonal Trend 
>**Example (Seasonal Trend):** Let $X_t=-2\cos(\pi t/5)+3\sin(\pi t/3)+W_{t}$, where $W_t\sim WN(0,4)$. Let's use 100 iterations.

```{r, fig.height = 10, fig.width = 9}
set.seed(100);  # This allows us to reproduce our results
par(mfrow=c(2,1)) #This gives us our graphs in 2 rows, 1 column


t=seq(1,100,1) #This gives our iterations starting from t=1 to t=100, with a step size of 1
St<-2*cos(pi*t/5)+3*sin(pi*t/3) #Periodic Trend
Wt<-rnorm(length(t),0,2) #White Noise
Zt<-St+Wt #Time series with seasonal component
plot(t,Zt,xlab="Time",ylab=expression(X[t]), main="Seasonal Trend") #This plots our data points
lines(t,St,col="red") #This draws the curve fit
acf(Zt, main="") #This plots the ACF
```

##Nonconstant Variance
>**Example (Random Walk):** Let $\displaystyle S_{t}=\sum_{j=1}^{t}X_{j}$, where $X_{t}\sim WN(0,1)$. Let's use 200 iterations.

```{r, fig.height = 10, fig.width = 9}
set.seed(100); # This allows us to reproduce our results
par(mfrow=c(2,1)) #This gives us our graphs in 2 rows, 1 column
t=seq(1,200,1) #This gives our iterations starting from t=1 to t=200, with a step size of 1
Xt1<-rnorm(length(t),0,1) #X_{t}\sim WN(0,1)
St1<-cumsum(Xt1) #Here is the random walk
plot.ts(St1,type="o",col="blue", xlab="Time",ylab=expression(S[t]), main="Random Walk") #This plots the random walk
acf(St1, main="") #This plots the ACF
```
