---
title: "Project 1 - Analysis of NYC Restaurant Prices"
author: "Jumpei Fujimoto"
output:
  html_notebook:
    theme: flatly
---

## Description of Project

In this project, you will use ordinary least squares regression to model the price at a restaurant using one of four possible predictors. The data is stored in the filed `nyc.txt`. This tab-separated text file contains information for 168 Italian restaurants in New York City. The dataset contains six variables for each restaurant: 

<center>
Variable | Description
-----|----------------------------------------------
**`Price`** | The average price, in USD, for a meal at the restaurant (including one drink and a tip).
**`Food`** | The average customer rating of the food, on a scale from 1 to 30. 
**`Decor`** | The average customer rating of the decor, on a scale from 1 to 30. 
**`Service`** | The average cusstomer rating of the service, on a scale from 1 to 30.  
**`Wait`** | The average wait time, in minutes, on a Saturday evening. 
**`East`** | A binary variable. Equals 1 if the restaurant is east of 5th Avenue, and 0 otherwise. 
</center>

We will not be using the `East` column in this project. 

## **Part A: Loading and Exploring the Data**

Use the `read.table()` function to read the data into a dataframe called `df`. Display a summary of this dataframe. 

```{r}
df <- read.table("nyc.txt", sep="\t", header = TRUE)
summary(df)
```



## **Part B: Graphical Analysis**

Use the `plot()` function to create a scatter plot of **price** against the **food rating**. Style the plot as follows: 

* Set `pch` to 21, set `bg` to a color of your choice, and set `col` to `black`.
* Label the `x` axis: "Customer Rating of Food"
* Label the `y` axis: "Price in $"
* Title the plot: "Relationship between Food Rating and Price"


```{r}
plot(df$Price ~ df$Service, pch=21, col="black", bg="salmon", ylab = "Price in $", xlab = "Customer Rating of Food", main = "Relationship between Food Rating and Price")
```

Create a scatter plot of **price** against the **decor rating**. Style the plot as describe previously, with the following modifications:

* Label the `x` axis: "Customer Rating of Decor"
* Title the plot: "Relationship between Decor Rating and Price"


```{r}
plot(df$Price ~ df$Decor, pch=21, col="black", bg="salmon", ylab = "Price in $", xlab = "Customer Rating of Decor", main = "Relationship between Decor Rating and Price")
```


Create a scatter plot of **price** against the **service rating**. Style the plot as described previously, with the following modifications:

* Label the `x` axis: "Customer Rating of Service"
* Title the plot: "Relationship between Service Rating and Price"



```{r}
plot(df$Price ~ df$Service, pch=21, col="black", bg="salmon", ylab = "Price in $", xlab = "Customer Rating of Service", main = "Relationship between Service Rating and Price")
```

Create a scatter plot of **price** against the **wait time**. Style the plot as described previously, with the following modifications:

* Label the `x` axis: "Average Wait Time (in min)"
* Title the plot: "Relationship between Wait Time and Price"



```{r}
plot(df$Price ~ df$Wait, pch=21, col="black", bg="salmon", ylab = "Price in $", xlab = "Average Wait Time(in min)", main = "Relationship between Wait Time and Price")
```



## **Part C: Create the Linear Models**

We will now generate four regression models. Each model will have `Price` as the response variable, and one of the other variables as the predictor. 

In the code chunk below, regress `Price` against `Food`, storing the resulting model in a variable called `mod1`. Display a summary of this model. 


```{r}
mod1 <- lm(df$Price ~ df$Food)
summary(mod1)
```

In the code chunk below, regress `Price` against `Decor`, storing the resulting model in a variable called `mod2`. Display a summary of this model. 

```{r}
mod2 <- lm(df$Price ~ df$Decor)
summary(mod2)
```


In the code chunk below, regress `Price` against `Service`, storing the resulting model in a variable called `mod3`. Display a summary of this model. 

```{r}
mod3 <- lm(df$Price ~ df$Service)
summary(mod3)
```

In the code chunk below, regress `Price` against `Wait`, storing the resulting model in a variable called `mod4`. Display a summary of this model. 

```{r}
mod4 <- lm(df$Price ~ df$Wait)
summary(mod4)
```

## **Part D: Summary of Models**

In each of the equations below, replace the zeros with the appropriate parameter estimate. Round all parameter estimates to 4 significant digits. 

$$\hat {Price} = -17.8321 + 2.9390 \cdot Food$$

$$\hat {Price} = -1.362 + 2.490 \cdot Decor$$
$$\hat {Price} = -11.9778 + 2.8184 \cdot Service$$
$$\hat {Price} = 39.88559 + 0.12265 \cdot Wait$$


## **Part E: Model Diagnostics**

Create a vector named `r2_vector` that contains the $r^2$ value for each of the four models (in the order in which the models were created). Name the entries of this vector `mod1`, `mod2`, `mod3`, and `mod4`. Display the vector. 


```{r}
r2_vector <- c(.3932, .5247, .4111, .01228)
names(r2_vector) <- c("mod1", "mod2", "mod3", "mod4")

r2_vector

```

Create a vector named `t_vector` that contains the value of the test statistic, t, for the hypothesis test $H_0: \beta_1 = 0$ for each of the four models (in the order in which the models were created). Name the entries of this vector `mod1`, `mod2`, `mod3`, and `mod4`. Display the vector. 

```{r}
t_vector <- c(10.371, 13.537, 10.764, 1.437)
names(t_vector) <- c("mod1", "mod2", "mod3", "mod4")

t_vector
```

List the models in the order of their p-values for this particular hypothesis test, from lowest to highest. 
1. Model 2
2. Model 3
3. Model 1
4. Model 4

**Replace this line with your answer.**


Create a vector named `rse_vector` that contains the value of $s$ for each of the four models (in the order in which the models were created). Name the entries of this vector `mod1`, `mod2`, `mod3`, and `mod4`. Display the vector. 

```{r}
rse_vector <- c(7.261, 6.426, 7.153, 9.263)
names(rse_vector) <- c('mod1', 'mod2', 'mod3', 'mod4') 

rse_vector
```

Display the standard deviation of the response variable. 

```{r}
sd <- sd(df$Price)
sd
```


## **Part F: Model Selection**

Based on the model diagnostics above, use the list below to rank the models in order from best to worst. 

1. Model 2
2. Model 3
3. Model 1
4. Model 4

Explain why you selected the model you did as the best model. Explain why you selected the model you did as the worst model. 

r2_vector is the key how to analyze the model because r2_vector explains how much percentage covered the variance by the model. At the case in mod4, r2_vector is loweset in those four models. It means that mod4 does not fit the most. On the contrary, the r2_vector of mod2 is the highest. It means that mod2 fits the most to the actual value.

**Replace this line with your answer.**

## **Part G: Residual Analysis**

We will now perform an analysis of the residuals in the model you identified as being the best model. In the code chunk below, create a vector `res` that stores the residuals for your selected model. Then create a residual plot for that model, with the following characteristics:

* Set `pch` to 21, set `bg` to a color of your choice, and set `col` to `black`.
* Select an appropriate label for the `x` axis.
* Label the `y` axis: "Residual"
* Title the plot: "Residual Plot"
* Add a horizontal line to your plot at $y=0$. 
* Color the line red, with `lwd` set to 2. 

```{r}
res <- mod2$residuals

plot(res ~ df$Decor, pch = 21, bg = "salmon", col = "black", 
     xlab = "Customer Rating of Decor", ylab = "Residual", 
     main = "Residual Plot")
abline(h = 0, col = "red", lwd = 2)
```

**Replace this line with your observations concerning the residual plot. Does it look good? Why or why not?**

We will now attempt to assess the normality of the residuals. Create a histogram of the residuals in your selected model. Set the histogram to have 20 breaks. Set the `col` parameter to a color of your choice. 

```{r}
hist(res, breaks = 20, col = "blue", 
     xlab = "Residuals", main = "Histogram of Residuals")
```

**Replace this line with your observations concerning the histogram. Does it look good? Why or why not?**

Ceate a qqplot plot of the residuals. 

```{r}
qqnorm(mod2$residuals)
qqline(mod2$residuals)
```

**Replace this line with your observations concerning the qqplot. Does it look good? Why or why not?**

## **Part E: Predictions**


Use your model to create predictions for the price at three restaurants with the following characteristics:

Food | Decor | Service | Wait
-----|-------|---------|-------
  16 |  21   |   16    |  37
  18 |   9   |   21    |  15
  21 |  14   |   18    |  31

With each prediction, provide a 90% prediction interval for the price. 

**Generate all three predictions with only one call of the `predict()` function.**

```{r}
Decor <- data.frame(Decor = c(21, 9, 14))
predict(lm(Price~Decor,df), Decor, interval = "predict", level = .90)
```



